---
title: "Alcohol vs Seat choice"
author: "Melanie Vera"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question 
Is there a difference between the alcohol consumed between the row you choose to sit in??

## Method
Predict alcohol consumption base on where you sit

$H_0$: There is no difference between the alcohol consumed between the row you choose to sit in.

$H_A$: There is a difference between the alcohol consumed between the row you choose to sit in

alcohol is numerical
set is categorical
We use the helper file

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The boxplot shows that people that sit in the back drink the most. 

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The mean for the people that sit in the back is 8.55. While the mean for the front is 1.78 and the mean for the back is 3.33. Showing that the back row is the one that has the most drinkers.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

This shows that our p value is 0.000116, which is lower than 0.05. Meaning that we reject the null hypothesis. 

```{r}
plot(TukeyHSD(model1))
```

The tukey shows that the middle-front have no difference, but the middle-back and the front-back show that there are a difference because 0 is not in the interval like middle-front.

## Conclusions

In conclusion we rejected the null hypothesis because the p value was 0.000116, which is less than 0.05. Meaning that there is a difference between the alcohol consumed between the row you choose to sit in. The boxplot shows that the people that side in the back are the people that drink the most. While the tukey test goes more indeep to show that the middle-front has no difference, while the middle-back and the middle-front do have a difference.
